To be FAIR: Theory Specification Needs an Update

### 2025-06-20 action_letter.Rmd
Update action_letter.Rmd
Update to the construct validity and nomological net comment

The second is that much of what we describe looks like Meehl's nomological nets. This is definitely true for the way that *we* are using FAIR theory (e.g., in the online examples), as we are inspired by Meehl,
but it's not necessarily true of FAIR theory in general. 
We agree that several psychological theories can be specified as a nomological network of abstract entities and empirical predictions/observations.
However, not all theories have been specified to such a level or need to be specified in such a way. 
As such, FAIR Theory accommodates nomological nets and construct validation endeavours, but is not identical to them. 
It is interesting to note that Cronbach and Meehl (1955) did talk about (proto)FAIR requirements:
"Whether or not an interpretation of a test’s properties or relations involves questions of construct validity is to be decided by examining the entire body of evidence offered, together with what is asserted about the test in the context of this evidence." (p.4)
"Hence, the investigator who proposes to establish a test as a measure of a construct must specify his network or theory sufficiently clearly that others can accept or reject it." (p.13)
"A consumer of the test who rejects the author’s theory cannot accept the author’s validation. He must validate the test for himself, if he wishes to show that it represents the construct as he defines it."
We're not sure if further changes need to be made to address this.

>>>>

The second is that much of what we describe looks like Meehl's nomological nets. This is definitely true for the way that *we* are using FAIR theory (e.g., in the online examples), as we are inspired by Meehl,
but it's not necessarily true of FAIR theory in general. 
We agree that several psychological theories can be specified as a nomological network of abstract entities and empirical predictions/observations.
However, not all theories have been specified in such a way or to such a level. 
Nor do we think that this is what we should strive for categorically.
As such, FAIR Theory accommodates nomological nets and construct validation endeavours, 
but is not identical to them. 
Thus, we decided not to mention nomological nets with respect to theory specification.
It is interesting to note that Cronbach and Meehl (1955) did talk about (proto)FAIR requirements:
"Whether or not an interpretation of a test’s properties or relations involves questions of construct validity is to be decided by examining the entire body of evidence offered, together with what is asserted about the test in the context of this evidence." (p.4)
"Hence, the investigator who proposes to establish a test as a measure of a construct must specify his network or theory sufficiently clearly that others can accept or reject it." (p.13)
"A consumer of the test who rejects the author’s theory cannot accept the author’s validation. He must validate the test for himself, if he wishes to show that it represents the construct as he defines it." (p.13)
We have incorporated these quotes as a footnote at the end of Section "The Need for FAIR Theory", which reads as follows:
